---
title: "ISLR_Chapter_02"
author: "Pankaj Kumar"
date: "12/23/2017"
output: html_document
---

Goal: Load a dataset in "College.csv" and format it so that columns represent actual metrics. We don't want college names as a columns in the dataset, because, it will not add any value in the data analysis. Instead, we would like to set the rownames by the college names.
```{r}
# loads the College.csv dataset to a variable.
college = read.csv("College.csv", header = T)
# sets the name for each of the rows. 
# In current case, we are setting the name of each row by the first column of the data set, i.e. 'college name' in this case.
# 
# For a data frame, rownames and colnames eventually call row.names and names respectively, but the latter are preferred.
rownames(college) = college[,1]
# update the college variable by removing the first column, i.e. by removing 'college name' in current case.
college = college[, -1]
college
```

Goal: we will perform some analysis on this dataset:
```{r}
summary(college)
# scatter plots for the first ten columns
pairs(college[, 1:10])
# creates a boxplot of Outstate vs Private
plot(college$Outstate, college$Private)
```

Goal: We want to create a qualitative variable called "Elite", by binning the "Top10perc" variable from the college dataset.

```{r}
# create a variable with value as "No" for nrow() count.
elite = rep("No", nrow(college))
# update the value of the variable list, depending on a condition. 
# In this case, we are updating Elite = "Yes", if the  column "Top10perc" in the "college" dataset has value greater than 50.
elite[college$Top10perc > 50] = "Yes"
# replacing "Yes" / "No" with Yes/No. (Optional, I guess.)
elite = as.factor(elite)

college = data.frame(college, elite)
college_with_elite = subset(college, elite=='Yes')
college_with_elite
nrow(college_with_elite)
```



